---
title: "Getting it together"
subtitle: "A land value capture idea"  
author: 
  - "Kay Seetal"
  - "Bertrand Bhikarry"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#1381B0",
  secondary_color = "#FF961C",
  inverse_header_color = "#FFFFFF"
)
```
```{r xaringan-webcam, include = FALSE}
xaringanExtra::use_webcam()
```



## An assumption 

.left-column[
##  1 ... of 3
]

.right-column[
**You want a Tobago holiday home**   

![](https://drive.google.com/uc?export=view&id=1ehyhB9WclXbVq9T8qTbObn1Wt-NwhV7k)

]

---
##  Another assumption 

.left-column[
## 2 ... of 3
]
.right-column[

![](https://drive.google.com/uc?export=view&id=1HA5XXfNfQ998gl9PTNszWk1aiQTXdu7v)

**You want it cheap** <br>Or perhaps just realistically priced.

]

---
name: assumption3

## Final assumption 

.left-column[
## 3 (of 3)
]
.right-column[

![](https://drive.google.com/uc?export=view&id=1cxNGR_8W8t7Za8DeUx1Ef42Soq3qbS-6)

**You got a few beans under the mattress** <br> and they interfere with a good night's sleep
]
---
class: center top

# If

.left-column[
### If any two (2) assumptions apply  

 And you are:
 
]

.right-column[
### Related to Kay or Bertrand

.footnote[*you may proceed* that one step nearer your idyll]

]
---
## Welcome

<center><img src="https://drive.google.com/uc?export=view&id=10DlYvg1H8ZWvFml3v0svg2fdCdpI0j2I" height="200px"></center>
  
#### Let's construct Six (6) Signature two-bedroom condo Style units in Tobago.

Think <br>**GREEN**<br>**GRAN CANARIA**<br>**STUDIO** 

---
## More

.left-column[**ABOUT THE LAND**]

.right-column[

  - Its part of the old Stables plot. 
  
  - Land under the units will be leased TO THE UNITS (*for **X** years*)
  
  .footnote[*Term of the lease is a negotiation point. **X** is less than the LOS leasehold*]
  
  ]

---
## Ownership

.left-column[Ownership is **Shares**]

.right-column[Each person buys into the deal as a director. <br>Shares are allocated via a registered company (*see footnote*) created for the purpose of financing and building the condos.<br>
Only unit holders can be directors.
<br> Unit is assigned to directors for period of the lease.
]

.footnote[*Get In Touch Co. obtains its lease from the owner Essentially Tobago Ltd*]
---
## The cost

.left-column[

#### Unit design

#### Borrowing costs]


.right-column[Design will influence/determine end price. I'd recommend identical units. Work with a round figure of $950. per sq foot for a turnkey unit.

Cost of loans will increase final figure for everyone. This is where [Assumption 3](#assumption3) kicks in. *Is this goodbye*?
]

---
## Snapshot of costs

.left-column[Essentially Tobago oversees the project throughout]

.right-column[
  - Land preparation (incl paving)
  - Water supply and Sewerage (incl drainage )
  - Electrical (initial connection)
  - Architect fees (if used)
  - Legal 
      + Conveyancing (contracts)
      + Isolating the parcel (land survey and lease)
  - Insurance (build phase)
  - Security system
      
      
  ]
---
## Running costs

.left-column[A reiteration. <br>Running costs after handover]
.right-column[ 

  - TTEC
  
  - WASA
  
  - WIFI
  
  - MAINTENANCE
  
  - SECURITY

]

.footnote[Fee-based maintenance falls to Essentially Tobago]
---

class: inverse center middle

# The Other Bigger Idea

---
## Capturing value

.pull-left[Now that you've got a signature property<br> Make the best of things. <br> Extend the GET IN TOUCH collective <br> Create more beans!!] 

.pull-right[
<img src ="https://drive.google.com/uc?export=view&id=1dYm15wCtBP3IfDqwg7c4XTD_KsQdUcuI" height = "350px">
<!--
![Get In Touch ](https://drive.google.com/uc?export=view&id=1dYm15wCtBP3IfDqwg7c4XTD_KsQdUcuI) -->
]

---
class: center middle

THANKS FOR LISTENING 


.footnote[contact name goes here]

---
